NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-25 results.tex
draft of aaz part

@@

@@

@@

>>>>

In close analogy with the previous two processes considered, 
we start our discussion of the results with the transverse 
momenta of the leading and subleading photon and the charged 
lepton pair, cf.\ Figure \ref{fig:aaz:pt}. 
The first observation is, while the general behaviour of the 
spectra is the same as in \aaw production, the inclusive QCD 
corrections are much smaller in this case. 
They range between $\deltaQCD=0.3-0.4$ for the leading and 
subleading photon and rise to 0.7 for the lepton pair at 
500\,GeV. 
The restrictive jet veto employed for the previous process 
reduces the QCD corrections further. 
Beyond the negligible impact at very small transverse 
momenta, they turn negative early on, reaching $\deltaQCD=-0.2-0.4$ 
at 500\,GeV. 
The electroweak corrections negative throughout, increasing 
from $\deltaEW=-5\%$ at low transverse momenta to $-20\%$ at 
500\,GeV.
They are consistently larger than the LO uncertainty estimate. 
As a consequence, the difference between the additive and 
multiplicative is comparably large, especially in the high 
\pT regions.

@@

Figure \ref{fig:aaz:myy} continues to display the invariant masses 
of the leading and subleading photon, and both the leading and 
subleading photon and the lepton pair. 
The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ is produced by 
configurations where the respective photon is emitted by the 
lepton-pair from a resonant $Z$ boson decay. 
Again, the QCD corrections are moderate, always staying below 
$\deltaQCD=0.4$ and of a similar shape as encoutered already in 
\aaw\ production. 
The jet veto again reduces the QCD correction and drives in negative 
in large portions of the observable range, reaching as much as 
$\deltaQCD=-0.5$ for the diphoton invariant mass. 
The electroweak corrections, on the other hand, are very similar 
to the \aaw case: with the exception of the well known positive 
radiative corrections below the $Z$ peak, they are negative 
throughout, reaching $\deltaEW=-20\%$ at invariant masses of 
1\,TeV.
As in the case of the transverse momenta, due to the similar size 
of the QCD and electroweak corrections at large transverse 
momenta, the difference between their additive and the multiplicative 
combination is amplified.

@@

In Figure \ref{fig:aaz:dphi} we consider the azimuthal separation 
between the leading and subleading photon, and both the leading 
and subleading photon and the lepton pair.
While the both photons tend to be back-to-back, the azimuthal 
separation of the leading photon and the lepton pair exhibits 
a kinematic edge at LO, restricting it to be larger than 
$\tfrac{1}{2}\,\pi$. 
\comment{MS: Do we understand why this is?}
On the contrary, the azimuthal separation of the subleading 
photon and the lepton pair exhibits no such limit at LO and 
instead peaks at roughly $\Delta\phi=\tfrac{1}{2}\,\pi$. 
The QCD corrections, with the exception of the aforementioned 
edge, are generally flat, taking values of $\deltaQCD\approx 0.3$ 
in the absence and $\deltaQCD\approx 0.2$ in the presence 
of a jet veto. 
The electroweak corrections are equally flat and amount to 
$\deltaEW\approx-4\%$. 
Their additive and multiplicative combinations are very 
similar.

@@

Finally, \aaz\ production is the only process of the three processes 
considered in this publication which can be produced through 
photon-induced channels at leading order, 
$\gamma\gamma\to\ell^+\ell^-\gamma\gamma$. 
To this end, we investigate their contribution at LO in 
Figure \ref{fig:aaz:aa-ind}. 
The photon-induced contribution is typically a few per mille of the 
LO cross section, but raises up to 2\% for invariant masses larger 
than 1\,TeV, especially $m_{\gamma_i\ell^+\ell^-}$. 
In this region, however, typical QCD and EW corrections are much larger 
such that this contribution can be safely ignored. 
As the photon-induced processes only contribute through non-resonant 
lepton-pair production, their contribution can be further suppressed 
by tightening the acceptance window in the lepton-pair invariant mass.
